%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{List of Publications}
   \setlength{\extrarowheight}{3pt}
	
\begin{cventries}
\vspace{-0.5cm}
\cventry
{ }
{ }
{ }
{ }
{ \begin{cvitems}
\small
	\setlength\itemsep{1.2em} 
\item[14.] Daniel Smith et al., {\bf (one of the contributing author)}, Non-linear Reconstruction of Information Modulated by Deterministic and Random Optical Fields - Concepts. \textbf{Journal of Imaging} \textit{(Invited manuscript - Under preparation)}.
\item[13.] {\bf P. A. Praveen}, T. Kanagasekaran, Impact of Furan Substitution on the Optoelectronic Properties of Biphenylyl/Thiophene  for Light Emitting Transistor Applications. \textbf{The Journal of Physical Chemistry A} 126 (4) (2022) 600.
\item[12.] V. Lakshmi Vennila, {\bf P. A. Praveen}, T. Kanagasekaran, N V L Narasimha Murty, Direct X-ray detection using thermally evaporated Pentacene Schottky diodes. \textbf{Journal of Instrumentation} 17 (2022) P02024.
\item[11.] {\bf P. A. Praveen}, A. Bhattacharya, T. Kanagasekaran, A DFT Study on the Electronic and Photophysical Properties of Biphenylyl/Thiophene Derivatives for Organic Light Emitting Transistors, \textbf{Materials Today Communications} 25 (2020) 101509.
\item[10.] {\bf P. A. Praveen}, R. Ramesh Babu, Evaluation of nonlinear optical properties from molecular descriptors of benzimidazole metal complexes by principal component analysis, \textbf{Journal of Molecular Graphics and Modeling} 93 (2019) 107447.
\item[9.] {\bf P. A. Praveen}, R. Ramesh Babu, P. Balaji, A. Murugadas, M.A. Akbarsha, Laser assisted anticancer activity of benzimidazole based metal organic nanoparticles, \textbf{Journal of Photochemistry \& Photobiology, B: Biology} 180 (2018) 218.
\item[8.] {\bf P. A. Praveen}, R. Ramesh Babu, K. Ramamurthi, Role of annealing on the structural and optical properties of nanostructured diaceto bis-benzimidazole Mn(II) complex thin films, \textbf{Spectrochimica Acta Part A: Molecular and Biomolecular Spectroscopy} 173 (2017) 800.
\end{cvitems}}

\vspace{-0.5cm}
\cventry
{ }
{ }
{ }
{ }
{ \begin{cvitems}
\small
	\setlength\itemsep{1.2em}
\item[7.] {\bf P. A. Praveen}, R. Ramesh Babu, Theoretical and experimental evaluation of structural and optical properties of novel zinc-benzimidazole metal complex doped in polystyrene matrices, \textit{AIP Conference Proceedings} 1832 (2017) 140038.
\item[6.] {\bf P. A. Praveen}, R. Ramesh Babu, K. Ramamurthi, Theoretical and experimental investigations on linear and nonlinear optical response of metal complexes doped PMMA films, \textbf{Materials Research Express} 4 (2017) 025024.
\item[5.] {\bf P. A. Praveen}, R Ramesh Babu, Effect of substituents on polarizability and hyperpolarizability values of benzimidazole metal complexes, \textit{AIP Conference Proceedings} 1731 (2016) 090013.
\item[4.] {\bf P. A. Praveen}, R. Ramesh Babu, K. Jothivenkatachalam, K. Ramamurthi, Spectral, morphological, linear and nonlinear optical properties of nanostructured benzimidazole metal complex thin films, \textbf{Spectrochimica Acta Part A: Molecular and Biomolecular Spectroscopy} 150 (2015) 280.
\item[3.] {\bf P. A. Praveen}, R. Ramesh Babu, K. Ramamurthi, Validation of PM6 and PM7 semiempirical methods on polarizability calculations, \textit{AIP Conference Proceedings} 1665 (2015) 609.
\item[2.] {\bf P. A. Praveen}, S. P. Prabhakaran, R. Ramesh Babu, K. Sethuraman, K. Ramamurthi, Low power optical limiting studies on nanocrystalline benzimidazole thin films prepared by modified liquid phase growth technique, \textbf{Bulletin of Materials Science} 38 (3) (2015) 645.
\item[1.] {\bf P. A. Praveen}, R. Ramesh Babu, S. P. Prabhakaran, K. Ramamurthi, Linear and nonlinear optical properties of Mn doped benzimidazole thin films, \textit{AIP Conference Proceedings} 1591 (1) (2014) 991.
\end{cvitems}}
\end{cventries}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\clearpage
%\cvsection{Articles Under Submission}
%   \setlength{\extrarowheight}{3pt}
%	
%\begin{cventries}
%\vspace{-0.5cm}
%\cventry
%{ }
%{ }
%{ }
%{ }
%{ \begin{cvitems}
%\small
%	\setlength\itemsep{1.2em} 
%\item[1.] {\bf P. A. Praveen}, Katsumi Tanigaki, T. Kanagasekaran, Light Emitting Ambipolar Field Effect Transistors of Biphenylyl-Tetrathiophene Single Crystals with Regio-Specific Emission in Orange Wavelength. Submitted to \textbf{ACS Applied Materials \& Interfaces}: \textit{Submitted}
%\end{cvitems}}
%\end{cventries}
%\newpage % Force a new page for looks
%\cvsection{Books}

%----------------------------------------------------------------------------------------
%	SECTION CONTENT
%----------------------------------------------------------------------------------------

%\begin{cventries}

%%------------------------------------------------

%\cventry
%{\textbf{P. A. Praveen}, R. Ramesh Babu} % Role
%{\textnormal{Semiempirical Modeling and Experimental Evaluation of Benzimidazole Based Metal-Organic Complexes for Nonlinear Optical Applications}} % Title
%{Springer} % Location
%{In Press} % Date(s)
%{{\it In the book} Theoretical Materials Design: Optimization, Simulation and Experimental Realization}

%\cventry
%{\textbf{P. A. Praveen}} % Role
%{\textnormal{Gravitational Waves Explained}} % Title
%{eI Trendz, Tiruchirappalli} % Location
%{2018} % Date(s)
%{ }

%%------------------------------------------------


%\end{cventries}
